Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2019-02-09 pkg/disttree/inst/draft/draft.Rnw
further revisions regarding the comment of the AE in the main manuscript and the rejoinder
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2458 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 3d50f9000476a0f25edaf2e24265d953cb86472f

To assess whether these differences in predictive performance are due to differences
in the topography, Figure~\ref{fig:all-map} shows a brief spatial summary of all
stations. Each station is illustrated by a symbol that conveys which
model performed best in terms of CRPS on the last 4~years of the data.
Additionally, the color of the symbol indicates the CRPS difference between 
distributional forest and the best-performing other model. Green signals that
the distributional forest performs better than the other models whereas red
signals that another model performs better. Overall the distributional forest
performs on par (gray) or better (green) for the majority of stations. Only
for a few stations in the north-east EMOS performs best, and in East Tyrol
the prespecified GAMLSS performs particularly well in the validation period
(2009--2012).

@@

\hlc{Similarly, the score-based distributional forests introduced in this manuscript
proved to be quite robust to the different distributional specifications considered.
While all specifications focus on capturing mean-variance effects note that these
parameters are never fully orthogonal but can actually become quite closely correlated
due to the censoring (or trunctation and/or zero-inflation considered in Supplement~A).

@@

The supplement shows that some of the differences in forecast skill from
Figure~\ref{fig:all-map} even out in the cross-validation with distributional
forests typically performing at least as well as the best of the other models at most
stations. In particular, this also includes three stations in East Tyrol
where the prespecified GAMLSS performs best in the single-split setting
(learning based on 1985--2008 and validation for 2009--2012). While part of
the performance difference can also be attributed to different
climatological characteristics in East Tyrol (that, unlike North Tyrol, is located
south of the main Alpine Ridge), the differences are greatly reduced for several
stations in East Tyrol by considering more splits in the full cross-validation.

>>>>

To assess whether these differences in predictive performance are due to differences
in the topography, Figure~\ref{fig:all-map} shows a brief spatial summary of all
stations. Each station is illustrated by a symbol that conveys which
model performed best in terms of CRPS on the last 4~years of the data.
Additionally, the color of the symbol indicates the CRPS difference between 
distributional forest and the best-performing other model. Green signals that
the distributional forest performs better than the other models whereas red
signals that another model performs better. Overall the distributional forest
performs on par (gray) or better (green) for the majority of stations. Only
for a few stations in the north-east EMOS performs best, and in East Tyrol
the prespecified GAMLSS performs particularly well in the validation period
(2009--2012).
\hlc{Note that differences in the results of East Tyrol compared to the rest of 
Tyrol could be (partly) due to East Tyrol lying in a different climate zone but 
could also be caused by the specific selection of learning and validation period
as only one single time split is considered. This will be discussed more
in detail in the following section.}

@@

\hlc{Similarly, the score-based distributional forests introduced in this manuscript
proved to be quite robust to the different distributional specifications considered.
While all specifications focus on capturing mean-variance effects note that these
parameters are never fully orthogonal but can actually become quite closely correlated
due to the censoring (or truncation and/or zero-inflation considered in Supplement~A).

@@

The supplement shows that some of the differences in forecast skill from
Figure~\ref{fig:all-map} even out in the cross-validation with distributional
forests typically performing at least as well as the best of the other models at most
stations. In particular, this also includes three stations in East Tyrol
where the prespecified GAMLSS performs best in the single-split setting
(learning based on 1985--2008 and validation for 2009--2012). 
\hlc{The differences are greatly reduced for several stations in East Tyrol by considering 
more splits in the full cross-validation. However, part of the performance difference can also 
be attributed to varying climatological characteristics in East Tyrol that, unlike North Tyrol,
is located south of the main Alpine Ridge. Therefore, effects could be more additive
and with less interactions than in North Tyrol and thus be captured more precisely by
an additive model such as GAMLSS, particularly with an appropriate prespecification of covariates.}
